title

### 2025-03-01 docs/_tex/index.tex
push up second draft

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{TeX Gyre Termes}
  \setmathfont[]{TeX Gyre Termes Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

One can speculate that the motivation to associate military veterans
with civic engagement and democracy may be intended to counter negative
perceptions and impressions given by the proportion of veteran service
members arrested for taking part in the events on January 6th
(\citeproc{ref-jensen2022a}{Jensen, Yates, and Kane 2022};
\citeproc{ref-loewenson2023}{Loewenson 2023};
\citeproc{ref-milton2021}{Milton and Mines 2021}). Especially with
regard to research demonstrating that willingness to support violent
efforts to overturn election results (in support of Trump) is, on
average, more common among veterans than among matched samples of
non-veterans (\citeproc{ref-pape2024}{Pape et al. 2024}). This is in
addition to a strengthened association portrayed in media outlets
between military veterans and militias
(\citeproc{ref-steinhauer2020}{Steinhauer 2020}). Prior research has
substantiated such a connection between veterans and militia groups. A.
Cooter (\citeproc{ref-cooter2024}{2024}) notes from her 3-year
ethnographic fieldwork among Michigan militia members that,
``\ldots approximately 40\% of militia leaders and 30\% of members had
previous military experience. Most of these veterans actively sought out
such groups, as opposed to being recruited by them''
(\citeproc{ref-cooter2024}{2024}; see also \citeproc{ref-cooter2013}{A.
B. Cooter 2013}). Thus, countering such associations by promoting a
different image of veterans to the mass public and veterans alike seems
like a reasonable motivation. Yet such speculation is just that.

That being said, the general public perception, attitudes, or even
stereotypes about military veterans are significant to consider.
Although military recruitment shows a downward trend as of late, public
perception of veterans are overwhelmingly positive
(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
Veterans are a particularly potent group where mention of veteran status
seems to have a positive, calming, or nullifying effect on attitudes.
For instance, recent research shows that, during his campaign in the
2020 Democratic Primaries, Pete Buttigieg's military background
mitigated discrimination against him when he was presented as a veteran
married to man (\citeproc{ref-magni2024}{Magni and Reynolds 2024}).
Similar research has also found that a candidate's veteran status
affords them better evaluations regarding competency in particular issue
areas (e.g., war competence) (\citeproc{ref-hardy2019}{Hardy et al.
2019}). Moreover, veteran status seems to mitigate or nullify usual
stigmas associated with mental illness. That is to say, there is
negative stigma associated with mental illness
(\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such stigma
incurs labor market discrimination (\citeproc{ref-hipes2016}{Hipes et
al. 2016}), but evidence suggests that veteran status overrides such
stigma and discrimination (\citeproc{ref-maclean2014}{MacLean and
Kleykamp 2014}). Or, in another light, mental illness is seemingly more
\emph{understandable} (i.e., permissible) for veterans given the
presumptive reasons for their mental strife. And media framing as such
plays an important role on public perception
(\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}).

@@

I expected item responses from these two scales to be inversely
correlated among the sample, but not mutually exclusive. Indeed, this is
what I find. Polychoric correlations between the trust and distrust
items negatively correlate as expected{[}\^{}See Appendix C{]}, as does
the correlation between the two sum score scales. Given the ordinal
nature of the variable items, I conducted a Spearman's rank correlation
test (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
Kendall's \(\tau = -0.39\)) between scores on the two scales for the AZ
items (For the local item scale score correlation: \(\rho = -0.52\),
\(95\%\) CI {[}-0.56, -0.48{]}; Kendall's \(\tau = -0.39\)). The
negative correlation between the trust and distrust items and scores
makes intuitive sense.

@@

\caption{\label{tbl-ttest}Mean Difference Effect of Treatment Compared
to Control Condition}

@@

Figure~\ref{fig-coef1} displays standard difference estimates of
confidence in elections by treatment condition (control condition as
reference). Figure~\ref{fig-coef1-1} displays two models for confidence
in elections in Maricopa County, AZ, and one's local area by treatment
condition; Figure~\ref{fig-coef1-2} displays four models for trust and
distrust in elections in AZ or one's local area by treatment condition

the treatment effect on both trust and distrust is clear. Although the
effect is only there when questions pertained to Maricopa County, AZ.
The treatment effect on trust and distrust is conditional on whether the
survey questions inquired about elections in Maricopa County, AZ.
Announcing efforts to recruit veterans and their families to work as
election staff and volunteers increases confidence in elections
administration in places outside of one's local area, but doesn't boost
confidence in elections within one's local area. However, bear in mind
that confidence in elections for one's local area is already higher than
for those outside. Thus, there's already less insecurity concerning
elections in one's local area, but publicized efforts to recruit
veterans to work as election staff and volunteers is a small but
positive step towards closing that gap in confidence for elections that
occur elsewhere.

I now turn to results examining those who held onto the belief that the
2020 election results were illegitimate. I think check to see if
recruiting veterans simply makes people feel safer at the polls.

@@

@@

  \begin{itemize}
  \tightlist
  \item
    The sample may not be generalizable to the population.
  \item
    It's hard to say whether merely mentioning veterans is enough, as
    compared to explicitly naming veterans as the target of particular
    recruitment efforts.
  \end{itemize}
\item
  Interpretation is also limited considering that no other particular
  group, or groups are compared directly against the veteran treatment
  vignette, i.e., additional vignettes for other comparable groups.
\item
  Moreover, results are limited by the survey questions, questionnaire
  design, and experimental stimulus (i.e., vignette) for two reasons. -
  First, the vignettes and many survey questions ask about Maricopa
  County, AZ specifically. Adding a specific county in the vignette adds
  in a factor that cannot be accounted for without additional treatments
  that eliminate the setting as a potential influence. Moreover, the
  specificity of the setting adds in even more unexplained error---some
  people may have attitudes about the county in question, others won't,
  while others may be muffed to consider a random county in the U.S.
  they've know nothing about. Adding the county undermines the
  confidence that treatment effects are solely attributable to veterans
  to an unknown degree. - Second, questions ask about one's own local
  community in addition to identical questions which asked about
  Maricopa County, AZ. Consequently, many questions within the
  questionnaire were duplicates with that one differences. This isn't
  uncommon in surveys, however in this case, it lengthened the survey to
  a degree that likely resulted in a higher drop off rate. More
  importantly, the quality of responses were likely diminished to some
  unknown extent. Although it is possible to compare questions asked
  about Maricopa County, AZ to questions about one's local area, the
  quality of that comparison is limited by the unknown extent of fatigue
  induced by answering the same questions twice. It wasn't just that
  some questions were asked multiple times, almost all of the questions
  were duplicated; after completing a long series on Maricopa County,
  participants then answered the same questions about the local
  community. The rate to which participants dropped from the survey is
  \_\_\_, which suggests fatigue as an important factor. Survey fatigue
  is a known issue that should be taken into consideration. Comparison
  of treatment effects between the MC series and the local area series
  is undermined by the unknown influence that fatigue would have on
  response choices. Any differences couldn't confidently be attributed
  to ``my area'' vs Maricopa county. We also can't determine whether
  treatment effects are sustained when comparing the Maricopa County
  series to the local area series asked subsequently. We would have to
  assume the setting as irrelevant, which we can't reasonably do.
\end{itemize}

@@

@@

The median age was 46 (mean age was 47). There was 51.7\% (n = 658)
women, 47\% (n = 598) men, and approximately 1.3\% who identified as
either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
A large proportion of the sample identified as White or Caucasian (n =
975, 76.65\%), while all other non-White respondents comprised 27.83\%
of the sample. Those who held a graduate level degree (e.g., Master's,
Doctorate, or Professional level) comprised 13\% of the sample; those
with either degree at the Associate or Bachelor's level comprised
36.24\%, while 22.25\% had some college but no degree; and 28.46\% had
either a high school level or equivalent education or less than high
school. The largest proportion of the sample identified as Democrat at
44.64\%, followed by Republicans at 42.59\%. The proportion of true
Independents was 12.78\%.

@@

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{TeX Gyre Pagella}
  \setmathfont[]{TeX Gyre Pagella Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{anyfontsize}
\usepackage{dcolumn} 
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

One can speculate that the motivation to associate military veterans
with civic engagement and democracy may be intended to counter negative
perceptions and impressions given by the proportion of veteran service
members arrested for taking part in the events on January 6th
(\citeproc{ref-jensen2022a}{Jensen, Yates, and Kane 2022};
\citeproc{ref-loewenson2023}{Loewenson 2023};
\citeproc{ref-milton2021}{Milton and Mines 2021}). Especially with
regard to research demonstrating that willingness to support violent
efforts to overturn election results (in support of Trump) is, on
average, more common among veterans than among matched samples of
non-veterans (\citeproc{ref-pape2024}{Pape et al. 2024}). This is in
addition to a strengthened association portrayed in media outlets
between military veterans and militias
(\citeproc{ref-steinhauer2020}{Steinhauer 2020}). Prior research has
substantiated such a connection between veterans and militia groups.
Cooter (\citeproc{ref-cooter2024}{2024}) notes from her 3-year
ethnographic fieldwork among Michigan militia members that,
``\ldots approximately 40\% of militia leaders and 30\% of members had
previous military experience. Most of these veterans actively sought out
such groups, as opposed to being recruited by them''
(\citeproc{ref-cooter2024}{2024}; see also
\citeproc{ref-cooter2013}{Cooter 2013}). Thus, countering such
associations by promoting a different image of veterans to the mass
public and veterans alike seems like a reasonable motivation. Yet such
speculation is just that.

That being said, the general public perception, attitudes, or even
stereotypes about military veterans are significant to consider.
Although military recruitment shows a downward trend as of late, public
perceptions of veterans are overwhelmingly positive
(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
Veterans are a particularly potent group where mention of veteran status
seems to have a positive, calming, or nullifying effect on attitudes.
For instance, recent research shows that, during his campaign in the
2020 Democratic Primaries, Pete Buttigieg's military background
mitigated discrimination against him when he was presented as a veteran
married to man (\citeproc{ref-magni2024}{Magni and Reynolds 2024}).
Similar research has also found that a candidate's veteran status
affords them better evaluations regarding competency in particular issue
areas (e.g., war competence) (\citeproc{ref-hardy2019}{Hardy et al.
2019}). Moreover, veteran status seems to mitigate or nullify usual
stigmas associated with mental illness. That is to say, there is
negative stigma associated with mental illness
(\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such stigma
incurs labor market discrimination (\citeproc{ref-hipes2016}{Hipes et
al. 2016}), but evidence suggests that veteran status overrides such
stigma and discrimination (\citeproc{ref-maclean2014}{MacLean and
Kleykamp 2014}). Or, in another light, mental illness is seemingly more
\emph{understandable} (i.e., permissible) for veterans given the
presumptive reasons for their mental strife. And media framing as such
plays an important role on public perception
(\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}).

@@

I expected item responses from these two scales to be inversely
correlated among the sample, but not mutually exclusive. Indeed, this is
what I find. Polychoric correlations between the trust and distrust
items negatively correlate as expected\footnote{See Appendix C}, as does
the correlation between the two sum score scales. Given the ordinal
nature of the variable items, I conducted a Spearman's rank correlation
test (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
Kendall's \(\tau = -0.39\)) between scores on the two scales for the AZ
items (For the local item scale score correlation: \(\rho = -0.52\),
\(95\%\) CI {[}-0.56, -0.48{]}; Kendall's \(\tau = -0.39\)). The
negative correlation between the trust and distrust items and scores
makes intuitive sense.

@@

\caption{\label{tbl-ttest}Mean Difference of Treatment Compared to
Control Condition}

@@

Figure~\ref{fig-coef1} displays standard difference estimates of
confidence in elections by treatment condition (control condition as
reference). Figure~\ref{fig-coef1-1} displays two models for confidence
in elections in Maricopa County, AZ, and one's local area by treatment
condition; Figure~\ref{fig-coef1-2} displays the same except
\emph{confidence} is decomposed into its two components, \emph{trust}
and \emph{distrust}. These figures merely illustrate the effect of the
treatment with respect to the relationship between trust and distrust;
ultimately confidence improves.

Confidence in elections was higher among those who read the treatment
vignette but remained conditional on whether the survey questions
inquired about elections in Maricopa County, AZ. This evidence suggests
that announcing efforts to recruit veterans and their families to work
as election staff and volunteers may increase confidence in elections
administration in places outside of one's local area, but may not boost
confidence in elections within one's local area.

\subsubsection{2020 Election Legitimacy
Beliefs}\label{election-legitimacy-beliefs}

I now turn to results examining the effect of the treatment on those who
held onto the belief that the 2020 election results were illegitimate.
First, reviewing responses to items that capture trust in elections, it
is easy to recognize the difference between the way 2020 election
deniers responded with respect to where elections were held.

\phantomsection\label{cell-fig-legit}
\begin{figure}[!t]

\caption{\label{fig-legit}Trust in elections by treatment among those
who refute the 2020 election results}

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit-1.png}}

Among those who belief the 2020 election results were illegitimate,
trust in Maricopa County, AZ elections was lower for each item compared
to items pertaining to elections within one's local area, regardless of
treatment condition. However, notably, trust that election technology
would be secure received the lowest confidence endorsement overall.
There was also a notable lack of trust that the voting process would be
fair relative to the other items.\footnote{What is interesting to note
  here is that the first three items regard the more human element of
  the election administration process, e.g., ensuring accuracy of
  counts, competence, and commitment of election workers. Although a
  neat line can't really be drawn between the first three and latter two
  items presented here, it is interesting to see a divergence of the
  usual high confidence placed in local area elections.} Now the
comparative difference in responses between those in the treatment group
compared to those in the control group appears substantial for items
pertaining to elections in Maricopa County, AZ.

\phantomsection\label{cell-fig-legit2}
\begin{figure}[!t]

\caption{\label{fig-legit2}Distrust in elections by treatment among
those who refute the 2020 election results}

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit2-1.png}}

Concerning distrust among those who refuted the 2020 election results,
responses items assessing one's expectation that election fraud would
occur reveal the same pattern. Although there is not as stark a
disparity between responses of those in the treatment and those in the
control, among those in the treatment group, there does appear to be
less expectation that election fraud would occur in Maricopa County, AZ.
Overall, review of responses to trust (Figure~\ref{fig-legit}) and
distrust survey items (Figure~\ref{fig-legit2}) does lend credence to
the impact of the treatment.

In order to substantiate the overall influence of the treatment on
confidence in elections, I regressed the dependent variable confidence
on legitimacy beliefs while controlling for partisanship.

\caption{\label{tbl-legit}Confidence in Elections by Treatment and
Legitimacy Beliefs}

\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-2} D{.}{.}{-2} } 
\\[-1.8ex]\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{Confidence in AZ Elections} & \multicolumn{1}{c}{w/Interaction} \\ 
\hline \\[-1.8ex] 
 Treatment & 0.18^{***}$ $(0.05) & 0.09$ $(0.06) \\ 
  Not Legitimate & -0.72^{***}$ $(0.07) & -0.86^{***}$ $(0.09) \\ 
  Republican & 0.11$ $(0.08) & 0.12$ $(0.08) \\ 
  Democrat & 0.17^{*}$ $(0.09) & 0.17^{**}$ $(0.09) \\ 
  Not Legitimate * Treatment &  & 0.27^{**}$ $(0.11) \\ 
  Constant & 0.03$ $(0.08) & 0.07$ $(0.08) \\ 
 N & \multicolumn{1}{c}{1,263} & \multicolumn{1}{c}{1,263} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.14} & \multicolumn{1}{c}{0.14} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.13} & \multicolumn{1}{c}{0.14} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.93 (df = 1258)} & \multicolumn{1}{c}{0.93 (df = 1257)} \\ 
F Statistic & \multicolumn{1}{c}{49.92$^{***}$ (df = 4; 1258)} & \multicolumn{1}{c}{41.24$^{***}$ (df = 5; 1257)} \\ 
\hline \\[-1.8ex] 
\multicolumn{3}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\ 
\end{tabular}

The first model in \ref{tbl-legit} shows that overall confidence in
elections (trust - distrust) among those who read the treatment vignette
was significantly (statistically) greater than those who read the
control, on average and netting out the effects of partisanship and
legitimacy beliefs. Democratic partisanship remains marginally
significant at \(90\%\) confidence level (\(p = 0.055\)). Not believing
the 2020 election of Joe Biden was legitimate is negatively associated
with confidence in elections. In order to assess the magnitude of this
interaction effect of the treatment on those who refuted the 2020
election results, I ran a model where confidence in elections was
regressed on the interaction between the treatment and legitimacy
beliefs, controlling for partisanship.

There's a positive interaction effect of the treatment vignette among
those who believe that the 2020 election was not legitimate, on average
and controlling for partisanship. This shows that the treatment effect
was most influential upon those who believe the 2020 election results
were illegitimate. The treatment alone does not reverse such beliefs,
but this shows where its influence is perhaps most potent.

@@

Publicized announcements that election officials are actively recruiting
former military service members to work as election staff and volunteers
is associated with slightly greater confidence in elections compared to
election worker recruitment announcements that do not explicitly mention
targeted recruitment of former military service members. Moreover,
increased levels of confidence is limited to elections beyond one's
local area and, of course, in anticipation of election night. Whether
the increase in confidence is sustained post-election night cannot be
inferred from these results.

Bear in mind that confidence in elections for one's local area is
already higher than for those beyond. Thus, there's already more
insecurity concerning elections elsewhere for whatever reason. In the
anticipatory period prior to national elections, publicized efforts to
recruit veterans to work as election staff and volunteers may be a
small, but positive, step towards reducing insecurity in elections that
occur elsewhere. Especially among those who maintained a steadfast
degree of distrust in elections. Despite a lack of evidence that
systematic electoral fraud had occurred in the 2020 election, a
substantial proportion of the population were unwilling to affirm the
legitimacy of the results. However, despite such legitimacy beliefs,
most were not consistent as they expressed varying levels of trust in
different aspects of elections administration.

These results speaks more to the influence that military veterans have
among those who distrust the electoral process and refute the legitimacy
of prior outcomes than it does to the public more generally. In general,
public confidence appears strongest when the elections under
consideration regard those within one's local community. Yet, such
strong confidence is not generalized outward to the institution of
elections administration as a whole. Insecurity in the integrity of the
electoral process and its administration may be naturally higher for
elections that occur further from home. Whether that is due to some
local favorability bias or some outward negativity bias is hard to say.
And seeing as how insecurity presents vulnerability, it is perhaps far
easier to inspire a general sense of distrust in the process and its
administration in places not near and around one's local area.

@@

  \begin{itemize}
  \tightlist
  \item
    The sample may not be generalizable to the population.
  \item
    It's hard to say whether merely mentioning veterans is enough, as
    compared to explicitly naming veterans as the target of particular
    recruitment efforts.
  \end{itemize}
\item
  Interpretation is also limited considering that no other particular
  group, or groups are compared directly against the veteran treatment
  vignette, i.e., additional vignettes for other comparable groups.
\item
  Results are limited by the survey questions, questionnaire design, and
  experimental stimulus (i.e., vignette) for two reasons:

  \begin{itemize}
  \tightlist
  \item
    First, the vignettes and many survey questions ask about Maricopa
    County, AZ specifically. Adding a specific county in the vignette
    adds in a factor that cannot be accounted for without additional
    treatments that eliminate the setting as a potential influence.
    Moreover, the specificity of the setting adds in even more
    unexplained error---some people may have attitudes about the county
    in question, others won't, while others may be muffed to consider
    any random county in the U.S. they know nothing about. Adding the
    county undermines the confidence that treatment effects are solely
    attributable to veterans to an unknown degree.
  \item
    Second, questions ask about one's own local community in addition to
    identical questions which asked about Maricopa County, AZ.
    Consequently, many questions within the questionnaire were
    duplicates with but one difference. This isn't uncommon in surveys,
    however in this case, it lengthened the survey to a degree that
    potentially resulted in a higher drop off rate. More importantly,
    the quality of responses were likely diminished to some unknown
    extent. Although it is possible to compare questions asked about
    Maricopa County, AZ to questions about one's local area, the quality
    of that comparison is limited by the unknown extent of fatigue
    induced by answering the same questions twice. It wasn't just that
    some questions were asked multiple times, almost all of the
    questions were duplicated. After completing a long series on
    Maricopa County, participants then answered the same questions about
    the local community. I haven't computed the rate to which
    participants dropped from the survey, yet items contain more missing
    values toward the end of the survey. Some participants dropped out,
    but some simply skipped a few items. The extent to which this
    occurred is minor, but it does suggest fatigue as a worthy of
    consideration.
  \end{itemize}
\end{itemize}

@@

\newpage

@@

The median age was 46 (mean age was \(47\)), \(51.7\%\) (\(n = 658\))
women, \(47\%\) (\(n = 598\)) men, and approximately \(1.3\%\) who
identified as either Non-binary/third gender (\(n = 7\)) or preferred
not to say (\(n = 9\)). A large proportion of the sample identified as
White or Caucasian (\(n = 975, 76.65\%\)), while all other non-White
respondents comprised \(27.83\%\) (\(n = 297\)) of the sample. Those who
held a graduate level degree (e.g., Master's, Doctorate, or Professional
level) comprised \(13\%\) of the sample; those with either degree at the
Associate or Bachelor's level comprised \(36.24\%\), while \(22.25\%\)
had some college but no degree; and \(28.46\%\) had either a high school
level or equivalent education or less than high school. The largest
proportion of the sample identified as Democrat at \(44.64\%\), followed
by Republicans at \(42.59\%\). The proportion of true
Independents\footnote{Independent `leaners' were grouped into the
  respective party affiliation in which they lean.} was \(12.78\%\).

\caption{\label{tbl-demog}Sample Demographics}

\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllll}
\toprule
\textbf{Demographic} & \textbf{N} & \textbf{Overall}  N = 1,287\textsuperscript{\textit{1}} & \textbf{Control}  N = 637\textsuperscript{\textit{1}} & \textbf{Treatment}  N = 650\textsuperscript{\textit{1}} \\ 
\midrule\addlinespace[2.5pt]
{\bfseries Age group} & 1,287 &  &  &  \\ 
    18-34 &  & 350 (27\%) & 170 (27\%) & 180 (28\%) \\ 
    35-54 &  & 480 (37\%) & 245 (38\%) & 235 (36\%) \\ 
    55-74 &  & 390 (30\%) & 198 (31\%) & 192 (30\%) \\ 
    75-85+ &  & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\ 
{\bfseries Gender} & 1,272 &  &  &  \\ 
    Male &  & 598 (47\%) & 289 (46\%) & 309 (48\%) \\ 
    Female &  & 658 (52\%) & 330 (52\%) & 328 (51\%) \\ 
    Other/Refused &  & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\ 
    NA &  & 15 & 8 & 7 \\ 
{\bfseries Race/Ethnicity} & 1,272 &  &  &  \\ 
    White &  & 975 (77\%) & 478 (76\%) & 497 (77\%) \\ 
    Asian &  & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%) \\ 
    Black &  & 164 (13\%) & 85 (14\%) & 79 (12\%) \\ 
    Other &  & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%) \\ 
    Hispanic &  & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%) \\ 
    American Indian &  & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%) \\ 
    NA &  & 15 & 8 & 7 \\ 
{\bfseries White or Non-White} & 1,272 &  &  &  \\ 
    Non-White &  & 297 (23\%) & 151 (24\%) & 146 (23\%) \\ 
    White &  & 975 (77\%) & 478 (76\%) & 497 (77\%) \\ 
    NA &  & 15 & 8 & 7 \\ 
{\bfseries Education} & 1,272 &  &  &  \\ 
    H.S. or less &  & 362 (28\%) & 174 (28\%) & 188 (29\%) \\ 
    Some college no degree &  & 283 (22\%) & 142 (23\%) & 141 (22\%) \\ 
    College degree &  & 461 (36\%) & 236 (38\%) & 225 (35\%) \\ 
    Postgraduate degree &  & 166 (13\%) & 77 (12\%) & 89 (14\%) \\ 
    NA &  & 15 & 8 & 7 \\ 
{\bfseries Party ID} & 1,268 &  &  &  \\ 
    Independent &  & 162 (13\%) & 83 (13\%) & 79 (12\%) \\ 
    Republican &  & 540 (43\%) & 262 (42\%) & 278 (43\%) \\ 
    Democrat &  & 566 (45\%) & 283 (45\%) & 283 (44\%) \\ 
    NA &  & 19 & 9 & 10 \\ 
{\bfseries Military Relation} & 1,272 &  &  &  \\ 
    No relation &  & 789 (62\%) & 394 (63\%) & 395 (61\%) \\ 
    Only family &  & 362 (28\%) & 182 (29\%) & 180 (28\%) \\ 
    Served w/fam &  & 64 (5.0\%) & 31 (4.9\%) & 33 (5.1\%) \\ 
    Served &  & 57 (4.5\%) & 22 (3.5\%) & 35 (5.4\%) \\ 
    NA &  & 15 & 8 & 7 \\ 
\bottomrule
\end{tabular*}
\begin{minipage}{\linewidth}
Independents do not identify nor 'lean' toward either political party\\
\textsuperscript{\textit{1}}n (\%)\\
\end{minipage}

\newpage

\subsection{Appendix C: Trust and Distrust}\label{sec-appendix-c}

Polychoric correlation is a measure of association between two ordered
categorical variables each assumed to represent (i.e., indicate, be
influenced by) two normally distributed, continuous, latent variables.
Due to the fact that each item is an ordered categorical variable
assumed to represent one of two latent constructs (i.e., trust or
distrust, respectively), I examined polychoric correlations between the
items used to construct each scale. In addition, one set of the trust
and distrust items pertained to Maricopa County, AZ, whereas the other
set of items were identical except that these items pertained to one's
local area.

Since the two sets of items (AZ items and Local items) are, in theory,
supposed to capture the same normally distributed continuous latent
variables, then the polychoric inter-item correlations should be
significantly associated, strong, and in the same direction for the
items that measure trust regardless of whether the items pertain to AZ
or one's local area (likewise for distrust). Simply, trust/distrust in
elections in AZ should strongly and positively be associated with
trust/distrust in elections in one's local area.

Additionally, the items that indicate trust should negatively correlate
with items that indicate distrust. Furthermore, the strength of the
negative correlations between trust and distrust should closely
approximate if not match.

\phantomsection\label{cell-fig-polycor}
\begin{figure}[h]

\caption{\label{fig-polycor}Polychoric Item Correlation Matrix}

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-polycor-1.png}}

Indeed, this is what is revealed by the correlation matrix
(Figure~\ref{fig-polycor}). Trust items correlate positively, strongly,
and are significant regardless of location at which the items pertain.
The same goes for distrust items. Also, items meant to measure trust
negatively correlate with the items that measure distrust. However, the
positive correlations are not nearly as high as would be expected
supposing that the items are nearly identical theoretical indicators of
the same hypothetical constructs, i.e., trust and distrust respectively.

If the items accurately measure trust/distrust in elections regardless
of where those elections are said to take place, then positive
correlations between the AZ and Local area items should approach perfect
correlation as though the same exact questions were asked twice. This
result, however, suggests that the location of which the survey items
pertain (and perhaps other factors) makes a substantial difference in
the pattern of responses, but also raises valid questions as to whether
the items accurately measure the latent variable constructs in the first
place.

@@

\bibitem[\citeproctext]{ref-cooter2013}
Cooter, Amy. 2013. {``Americanness, {Masculinity}, and {Whiteness}: {How
Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.
